\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{parskip}
\usepackage{fontawesome5}

% Set Times New Roman as main font - ATS friendly
\usepackage{newtxtext,newtxmath}

% Page margins - optimized for ATS
\geometry{left=2cm,right=2cm,top=2cm,bottom=2cm}

% Professional Colors - Navy Blue Theme
\definecolor{headerblue}{RGB}{0,51,102}
\definecolor{accentblue}{RGB}{41,98,255}
\definecolor{textgray}{RGB}{51,51,51}

% Section titles - simple and ATS friendly
\titleformat{\section}{\large\bfseries\color{headerblue}}{}{0em}{}[\vspace{0.2em}\titlerule\vspace{0.3em}]

% Subsection titles
\titleformat{\subsection}{\normalsize\bfseries\color{headerblue}}{}{0em}{}[\vspace{0.2em}]

% Subsubsection for project titles
\titleformat{\subsubsection}{\normalsize\bfseries\color{headerblue}}{}{0em}{}[\vspace{0.1em}]

% Itemize with optimized spacing
\setlist[itemize]{leftmargin=*,label={$\bullet$},itemsep=0.2em,parsep=0pt,topsep=0.2em}
\setlist[description]{leftmargin=0em,labelwidth=0pt,itemsep=0.3em,font=\normalfont\bfseries}

% Hyperlink setup - ATS compatible
\hypersetup{
    colorlinks=true,
    linkcolor=accentblue,
    urlcolor=accentblue,
    pdfborder={0 0 0}
}

% Remove page numbers
\pagestyle{empty}

% Custom commands
\newcommand{\experienceheader}[2]{%
    \subsection{#1 \hfill #2}
}

\newcommand{\companyname}[1]{%
    \textbf{#1}
}

\begin{document}

% Header - With icons and hyperlinks (as requested)
\begin{center}
    {\huge\bfseries\color{headerblue} VIGNESH S}\\[0.3em]
    {\large\color{headerblue} Software Engineer}\\[0.6em]
    \begin{tabular}{c c c c c}
        \faPhone\ \href{tel:+919677362774}{+91-9677362774} & 
        \faEnvelope\ \href{mailto:vigneshsl.career@gmail.com}{vigneshsl.career@gmail.com} & 
        \faLinkedin\ \href{https://linkedin.com/in/vignesh-softwaredev}{LinkedIn} & 
        \faGithub\ \href{https://github.com/vigneshsl}{GitHub} & 
        \faGlobe\ \href{https://tinyurl.com/vigneshcareers}{Portfolio}
    \end{tabular}
\end{center}

\vspace{0.3em}
{\color{headerblue}\hrule height 1.5pt}
\vspace{0.5em}

% Professional Summary
\section{PROFESSIONAL SUMMARY}
Results-driven Software Engineer with 3 years of experience in industrial automation and embedded systems development. Skilled in \textbf{C++, MFC, WIN32API, and EPKS (Experion Process Knowledge System)} with a proven ability to deliver mission-critical control system solutions. Improved developer productivity by \textbf{50 percent} through automation tools and scripting. Experienced in the full \textbf{Software Development Life Cycle (SDLC)}, including requirements analysis, system design, implementation, testing, and documentation. Strong domain knowledge in process control systems, UI development, and real-time industrial-grade software, including \textbf{UOC and ACE controller} integration.


% Technical Skills
\section{TECHNICAL SKILLS}

\textbf{Programming Languages and Technologies:} C++, WIN32API, Batch Script, MFC, QT, QML

\textbf{Development Tools and Frameworks:} Visual Studio, ClearCase, Coverity, Inno Setup Compiler, MFC, QT Framework  

\textbf{Platforms and Systems:} Windows Development, Experion Process Knowledge System, Physical and Virtual UOC, ACE Simulation  

\textbf{Agile Practices:} Unit Testing, Integration Testing, System Testing, Code Review, Quality Assurance, Debugging  


% Key Achievements
\section{KEY ACHIEVEMENTS}
\begin{itemize}
    \item \textbf{Process Automation Excellence:} Developed comprehensive internal workflow automation solutions, reducing manual workload by 50 percent using custom batch scripting, Python programming, and C++ development.
    
    \item \textbf{UI Development:} Designed a dynamic Motor block user interface using the MFC framework, significantly improving configuration usability and user experience.
    
    \item \textbf{System Recovery and Maintenance:} Successfully recovered Unit Operations Controller (UOC) from failure states during development cycles, ensuring continuous system availability and minimizing downtime.

    \item \textbf{System Configuration Management:} Configured and optimized Experion Process Knowledge System (EPKS) environments for multiple controller models including Model 530 and Model 520, ensuring optimal functionality, performance, and reliability.
    
    \item \textbf{Legacy System Migration:} Successfully converted legacy Graphical User Interface (GUI) tools to lightweight Command Line Interface (CLI) applications, improving system performance, maintainability, and resource efficiency.
    
    \item \textbf{Deployment Optimization:} Streamlined software deployment processes using Inno Setup Compiler for faster and error-free releases, reducing deployment time and improving reliability.
\end{itemize}

% Professional Experience
\section{PROFESSIONAL EXPERIENCE}

\experienceheader{Software Engineer}{January 2023 - Present}
\companyname{Utthunga Technologies}

\vspace{0.4em}
\subsubsection{EPKS Control Builder Block Development}

\textit{Project Focus:} Software development and implementation of control system blocks for process automation, enhancing functionality and efficiency of the Experion Process Knowledge System (EPKS) through specialized industrial control blocks.

\vspace{0.2em}
\textbf{Responsibilities and Achievements:}
\begin{itemize}
    \item Collaborated with cross-functional teams to perform requirements analysis for functional and technical specifications of industrial control blocks.
    
    \item Designed and developed software blocks following industry coding standards, best practices, and Software Development Life Cycle (SDLC) methodologies.
    
    \item Executed comprehensive unit testing, integration testing, system testing, and bug resolution using debugging tools and quality assurance protocols.
    
    \item Authored technical documentation and software documentation, and participated in peer code reviews for quality control and knowledge sharing.
    
    \item \textbf{Enhanced developer productivity by 50 percent} through custom automation tools for XML generation, code templates, and workflow optimization.
    
    \item Implemented user interface solutions using Microsoft Foundation Classes (MFC) framework for Motor block configuration and system management.
    
    \item Developed custom error handling systems and description management functionality within the Experion Process Knowledge System (EPKS) station.
    
    \item Automated repetitive block development tasks through custom scripting solutions to handle operations including ACE Controller management and system maintenance.
    
    \item Configured Experion Process Knowledge System (EPKS) environments and managed Unit Operations Controller (UOC) recovery processes for continuous system availability.
    
    \item Developed WIN32 Application Programming Interface (API) solutions for block extensions and system integration.
    
    \item Performed code reviews and maintained code quality standards through static analysis tools and best practices.
    
    \item Implemented version control workflows using ClearCase for source code management and team collaboration.
\end{itemize}

\vspace{0.2em}
\textbf{Technology Stack:} C++, XML, Microsoft Foundation Classes (MFC), Batch Scripting, EPKS Configuration Studio, ClearCase Version Control, Visual Basic for Applications (VBA), Python, WIN32 Application Programming Interface (API), Inno Setup Compiler, Firmware Management Tools

\textbf{Controllers:} Physical Unit Operations Controller (UOC), Virtual Unit Operations Controller (vUOC), Simulation ACE

\vspace{0.5em}
\subsubsection{NOJA DCM Project}

\textit{Project Focus:} Worked on NOJA Power next-generation Device Configuration Management (DCM) software, designed to support Relay 4 protection modules and streamline configuration workflows through modern user interface and user experience design and direct device interaction.

\vspace{0.2em}
\textbf{Responsibilities and Achievements:}
\begin{itemize}
    \item Identified and resolved critical bugs and defects, improving system performance and reliability.
    \item Migrated legacy Graphical User Interface (GUI) tools to Command Line Interface (CLI) applications for improved maintainability and resource efficiency.
    \item Enhanced application performance through code optimization and refactoring.
    \item Collaborated with quality assurance team to ensure comprehensive testing coverage.
\end{itemize}

\vspace{0.2em}
\textbf{Technology Stack:} QT Framework, QML

% Education
\section{EDUCATION}

\textbf{Bachelor of Computer Applications (BCA)} \hfill \textbf{Expected Graduation: 2026}\\
Bharathidasan University \hfill 2024 - Present\\
Status: Currently pursuing (Second year completed)

\vspace{0.2em}
\textbf{Diploma in Computer Engineering (DCE)} \hfill \textbf{Graduated: 2022}\\
DOTE - Ramakrishna Mission Polytechnic College \hfill \textbf{Achievement:} 92 percent\\


% Certifications
\section{CERTIFICATIONS}
\begin{itemize}
    \item Programming Foundations: Conducting Code Reviews - LinkedIn Learning - September 2025
    \item C++ Essential Training - LinkedIn Learning - September 2025
    \item Windows Programming using Visual C++ and MFC - Udemy - August 2025
    \item Agile Software Development - LinkedIn Learning and CompTIA - September 2025
    \item Agile Software Development - LinkedIn Learning and PMI REP - September 2025
\end{itemize}

% Additional Information
\section{ADDITIONAL INFORMATION}

\textbf{Professional Experience:} 3 years in Industrial Software Development

\textbf{Domain Expertise:} Industrial Automation, Control Systems, Embedded Systems, Process Automation, Real-Time Systems, Process Control

\textbf{Core Competencies:} Rapid Learning, Automation-Driven Development, User Interface Design, Productivity Enhancement, Problem-Solving, Team Collaboration, Project Management, Technical Documentation, Code Review

\textbf{Languages:} Tamil (Native), English (Professional Working Proficiency)

\end{document}